Verifying synchronous distributed algorithms using IVy

### 2018-08-05 paper/paper.tex
explaining in a paragraph why it is useful to verify distributed algorithms ..as they are designed and proved by hand. Then, in a second paragraph a short explanation about the difference of automatic and deductive verification, and how it is unfeasible to apply automatic verification to distributed algorithms (due to them being parameterized, and parameterized verification is undecidable in general [1]).
Finally, say how Ivy is tailored to dealing with
these kinds of algorithms, and is a tool that allows the user to provide
invariants and check them automatically.

Also, an outline of the res

\lettrine[nindent=0em,lines=3]{I} t's a fascinating idea: taking any (distributed) algorithm and feeding it to
some powerful tool that evaluates it's correctness automatically. However, the problem of verifying infinite state systems
has not been effectively automated. Most of the systems currently in place require a user to annotate the
specification with inductive invariants. IVy does not solve this problem directly, but instead aims to increase user friendliness.

IVy's underlying hypothesis is that ``automated methods are difficult to apply in practice not primarily because they are unreliable, but because they are opaque''; meaning that they fail in ways inexplicable to the user. In light of this, the IVy system was designed to display proof-failure comprehensively to the human user, making the root cause of errors more visible. \cite[ p.1]{ivy}

This paper will give an introduction to the IVy system and its language. It will explain the paradigms underlying the automatic verification tool, its language and the context in which it may be employed.

\textit{Floodset}, a simple distributed algorithm, will be explained and used as an example to illustrate the strengths and limitations of the IVy system in verifying algorithms operating in a network. The goal of this work is to give readers a foundational understanding of IVy and a head start in verifying their own distributed algorithms.

@@

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------
\begin{thebibliography}{99}
    \bibitem{ivy} O. Padon, K. McMillan, A. Panda, M. Safiv, S. Shoham, ``Ivy: Safety Verification by Interactive Generalization'', Available \textit{https://www.cs.tau.ac.il/~odedp/ivy.pdf}
    \bibitem{refLanguageDoc} ``The IVy language'',  \textit{http://microsoft.github.io/ivy/language.html} [Accessed: 5.06.18], 2017
    \bibitem{invariants} ``Invariants'',  \textit{http://microsoft.github.io/ivy/examples/client\_server\_example.html} [Accessed: 5.06.18], 2017
    \bibitem{decid} ``Decidability'',  \textit{http://microsoft.github.io/ivy/decidability.html} [Accessed: 5.06.18], 2017
    \bibitem{refNancy} N. Lynch, ``Distributed algorithms'', 1996, San Francisco: Morgan Kaufmann Publishers
    \bibitem{github} C. Claus, ``BA'', \textit{https://github.com/calvinclaus/ba}, 2018
\end{thebibliography}

>>>>

\lettrine[nindent=0em,lines=3]{D}istributed algorithms is a class of algorithms that is designed to run on a set of distributed processors. They solve important problems in distributed systems such as leader election, resource allocation and \textbf{consensus}. Consensus algorithms aim to create agreement among a set of processors. For example, an airplane may posses a redundant set of sensors measuring the same quantity. They must finally agree on a value that is as accurate as possible, while being able to handle failure of a subset of sensors. To establish agreement between sensors a distributed consensus algorithm may be used.  Currently these algorithms are proven by hand. In light of the relevance of distributed algorithms, it is useful to automatise the process of proving their correctness.

  \textit{Automatic verification} takes an algorithm and exhaustively checks if the algorithm satisfies some specification. While this approach is conveniently fully automatic it is not applicable to infinite state systems as their state-space can, by definition, not be exhaustively searched. It is therefore not generally applicable to \textit{parameterized} distributed (consensus) algorithms, which take the number of processors communicating as a parameter.\cite{limits}

  On the other hand, \textit{deductive verification} takes an algorithm and some invariant. It proves the invariant is inductive with respect to the algorithm. If the invariant implies the correctness of the algorithm, the algorithm has been proven correct. This process does not exhaustively search all possible states and is therefore applicable to distributed (consensus) algorithms, however it relies on the user to annotate invariants.

  Ivy is tailored to simplify deductive verification of parameterized distributed algorithms. There are a variety of systems currently implementing the deductive verification process. IVy makes use of the same underlaying principle, but it aims to increase user friendliness of the verification process.  IVy's hypothesis is that ``automated methods are difficult to apply in practice not primarily because they are unreliable, but because they are opaque''; meaning that they fail in ways inexplicable to the user. In light of this, the IVy system was designed to display proof-failure comprehensively to the human user, making the root cause of errors more visible. \cite[ p.1]{ivy}

  This paper will give an introduction to the IVy system and its language. It will explain the paradigms underlying the automatic verification tool, its language and the context in which it may be employed.  \textit{Floodset}, a simple distributed algorithm, will be explained and used as an example to illustrate the strengths and limitations of the IVy system in verifying algorithms operating in a network. First \textit{Floodset} will be manually proven and then deductively verified.  The goal of this work is to give readers a foundational understanding of IVy and a head start in verifying their own distributed algorithms.

@@

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------
\begin{thebibliography}{99}
    \bibitem{limits} K. Apt, D. Kozen ``Limits of Automatic Verification of Finite-State Concurrent Systems'', 1986, Available \textit{http://www.cs.cornell.edu/~kozen/Papers/LimitsForAutomatic.pdf}
    \bibitem{ivy} O. Padon, K. McMillan, A. Panda, M. Safiv, S. Shoham, ``Ivy: Safety Verification by Interactive Generalization'', Available \textit{https://www.cs.tau.ac.il/~odedp/ivy.pdf}
    \bibitem{refLanguageDoc} ``The IVy language'',  \textit{http://microsoft.github.io/ivy/language.html} [Accessed: 5.06.18], 2017
    \bibitem{invariants} ``Invariants'',  \textit{http://microsoft.github.io/ivy/examples/client\_server\_example.html} [Accessed: 5.06.18], 2017
    \bibitem{decid} ``Decidability'',  \textit{http://microsoft.github.io/ivy/decidability.html} [Accessed: 5.06.18], 2017
    \bibitem{refNancy} N. Lynch, ``Distributed algorithms'', 1996, San Francisco: Morgan Kaufmann Publishers
    \bibitem{github} C. Claus, ``BA'', \textit{https://github.com/calvinclaus/ba}, 2018
\end{thebibliography}
